```{r}
x <-rnorm(20,0,1)
summary(x)
pnorm(10,0,1)
```
p calculates cumulative distribution functions
pnorm(q) = phi(q)
qnorm(p) = phi^-1(p)

```{r}
set.seed(1)
rnorm(10)
rnorm(10)
```
set.seed() reproduce random numbers

```{r}
set.seed(10)
x <- rep(0:1, each = 5)
x
e <- rnorm(10, 0, 20)
e
y <- 0.5 + 2 * x + e
y
plot(x,y)
```

```{r}
system.time(read.csv(file = "specdata/001.csv"))
hilbert <- function(n) {
i <- 1:n
1 / outer(i - 1, i, "+")
}
x <- hilbert(1000)
system.time(
  svd(x)
)
system.time(readLines("https://www.jhsph.edu"))
```
user time(CPU time) > elapsed(wallclock time), because linear algebra models use multi-threading/processors
user time(CPU time) < elapsed(wallclock time), because readLines takes smaller CPU time for execution, but the network part on bringing data from the webpage takes the rest of the time.

```{r}
read.csv("specdata/001.csv")
Rprof()
x <- read.csv("specdata/001.csv")
Rprof(NULL)
summaryRprof()

```


# Programming Assignment

## Actual solution is in Week 4 folder
```{r eval=FALSE, include=FALSE}
rout <- function(out){
#outcome_temp<- read.csv("op_pgass3.csv",colClasses = "character")
outcome_temp <- read.csv("rprog_data_ProgAssignment3-data/outcome-of-care-measures.csv", colClasses = "character")
names(outcome_temp)[11] <- "heart attack"
names(outcome_temp)[17] <- "heart failure"
names(outcome_temp)[23] <- "pneumonia"
outcome_temp <- outcome_temp[,c(2,7,11,17,23)]
outcome_temp[outcome_temp=="Not Available"] <- NA
outcome_temp$`heart attack`<- as.numeric(outcome_temp$`heart attack`)
outcome_temp$`heart failure`<- as.numeric(outcome_temp$`heart failure` )
outcome_temp$pneumonia <- as.numeric(outcome_temp$pneumonia )

outcome_temp[ , c("Hospital.Name","State",out)]
}

bestq <- function(st,out){

outcome_temp <- rout(out)

outcomes_list = c("heart attack","heart failure","pneumonia")
if(! out %in% outcomes_list) stop("invalid outcome")
#outcome_temp <- read.csv("op_pgass3.csv",colClasses = "character")

state_list <- unique(outcome_temp$State)
if (! st %in% state_list) stop("invalid state")

op1 <- outcome_temp[outcome_temp$State==st, ]
op1 <- na.omit(op1)
op1[order(op1[out],op1$Hospital.Name), ]$Hospital.Name[1]
}

rankHospital <- function(st,out,num="best"){
outcome_temp <- rout(out)
outcomes_list = c("heart attack","heart failure","pneumonia")
if(! out %in% outcomes_list) stop("invalid outcome")

state_list <- unique(outcome_temp$State)
if (! st %in% state_list) stop("invalid state")

op1 <- outcome_temp[outcome_temp$State==st, ]
op1 <- na.omit(op1)
op1$rank <- NA
op1$rank[order(op1[out],op1$Hospital.Name)] <- 1:nrow(op1)
if(num=="best")
{
  num <- min(op1$rank)
} else if(num=="worst") {
  num <- max(op1$rank)
}

op1[op1$rank==num, ]$Hospital.Name[1]

}

rankall <- function(out,num="best"){
  outcome_temp<- rout(out)
  outcomes_list = c("heart attack","heart failure","pneumonia")
  if(! out %in% outcomes_list) stop("invalid outcome")
  
   getnum <- function(df_col){
    if(num=="best")
    {
      num <- min(df_col)
    } else if(num=="worst") {
      num <- max(df_col)
    } else{
      num
    }
 }
  
  op_df <- data.frame()
  vect<- vector()
  op_df
  for (st in split(outcome_temp,outcome_temp$State)) {
    
    st <- na.omit(st)
    st$rank <- NA
    st$rank[order(st[out],st$Hospital.Name)] <- 1:nrow(st)
    num1 <- getnum(st$rank)
    st_1 <- st[st$rank==num1, ]
    
    op_df <- rbind(op_df, data.frame(hospital=st_1$Hospital.Name[1],state =st$State[1]))
  }
    
    rownames(op_df) <- op_df$state
    #print(rownames(op_df))
    op_df
    #split(outcome_temp,outcome_temp$State)
}

head(rankall("heart attack", 20), 10)
tail(rankall("pneumonia", "worst"), 3)
tail(rankall("heart failure"), 10)
rankall("heart attack",4)

r <- rankall("heart attack", 4)
as.character(subset(r, state == "HI")$hospital)
r <- rankall("pneumonia", "worst")
as.character(subset(r, state == "NJ")$hospital)
r <- rankall("heart failure", 10)
as.character(subset(r, state == "NV")$hospital)

bestq("AL","heart attack")
bestq("SC", "heart attack")
bestq("NY", "pneumonia")
bestq("AK", "pneumonia")
rankHospital("TX","heart failure",4)
rankHospital("MD", "heart attack", "worst")
rankHospital("MN", "heart attack", 5000)
rankHospital("NC", "heart attack", "worst")
rankHospital("WA", "heart attack", 7)
rankHospital("TX", "pneumonia", 10)
rankHospital("NY", "heart attack", 7)
rankHospital("AK","heart attack",20)
rankHospital("WI", "pneumonia", "worst")
```


